\label{sec:discussion}

The results show that resource-constrained model selection is a multi-objective
engineering decision. Qwen2.5-7B-Instruct and Qwen3-8B are currently the best
accuracy-oriented choices, but their memory footprints and latency are not
always necessary for a terminology-heavy local assistant. Conversely,
Qwen3-0.6B and Qwen3-1.7B are much cheaper to run and may be sufficient for
frequent bilingual term lookup or classroom demonstrations.

The efficiency table also cautions against treating quantization as a universal
speedup. Int4 reduces memory clearly for the Qwen3 models, yet bf16 is faster
on the tested prompt set. Int8 is generally the slowest path in the current
environment. This behavior is plausible because quantized inference depends on
kernel support, dequantization overhead, batch size, and sequence length. For
deployment, the correct question is therefore not whether int4 is theoretically
smaller, but whether its measured memory saving is worth its observed latency
cost on the target machine.

The QLoRA results should be interpreted conservatively. The adapter training
and evaluation path is operational, and the Qwen2.5 adapted export preserves
public benchmark scores close to the baseline. However, the current Domain QA
summary uses one sample, so it cannot estimate real railway-domain accuracy.
The next draft should replace this sanity check with full-test exact-match
scores, qualitative error categories, and examples of terminology or regulation
phrases that improve after adaptation.

There are several limitations. First, the reported hardware is one GPU class,
so the measured speed may differ on Ada, Hopper, consumer laptop GPUs, or CPU
edge devices. Second, the current completed public results cover six models,
while the planned formal model pool contains nine models and the broader local
cache contains additional models reserved for future extension. Third, the
railway-domain evaluation requires stronger answer normalization because exact
match can underestimate correct translations with acceptable wording variants.
Finally, the paper does not propose a new algorithm; its value is in
deployment-oriented measurement, dataset construction, and transparent
separation of completed results from pending experiments.

Despite these limitations, the draft already provides useful practical
guidance. A laboratory that wants a strong single-GPU baseline should begin
with Qwen2.5-7B-Instruct or Qwen3-8B. A laboratory that wants the cheapest
interactive model should start with Qwen3-1.7B or Qwen3-0.6B. A laboratory that
wants a balanced QLoRA candidate should prioritize Qwen3-4B and Qwen2.5-7B,
then rerun the full railway-domain test set before making a final deployment
choice.
