\label{sec:experimental_setup}

\textbf{Hardware and software.} All experiments are designed for a single NVIDIA RTX 3090 GPU with 24GB of VRAM. The codebase is implemented in PyTorch and uses Hugging Face Transformers for model loading and generation, PEFT for parameter-efficient training, BitsAndBytes for low-bit quantization, and the Language Model Evaluation Harness for standardized benchmark execution. The recommended runtime environment is an isolated Conda environment under Ubuntu with CUDA-enabled PyTorch, which improves reproducibility and avoids package conflicts during fine-tuning and benchmark execution.

\textbf{Model pool.} The evaluated model pool contains seven open models: Qwen3-0.6B, Qwen3-1.7B, Qwen3-4B, Qwen3-8B, Qwen2.5-7B-Instruct, DeepSeek-R1-Distill-Qwen-7B, and Gemma 3 4B. This set intentionally covers three types of variation. First, it spans a meaningful parameter range from sub-1B to 8B. Second, it includes both mainstream instruction-tuned models and reasoning-oriented distilled models. Third, it includes both Chinese-strong and internationally popular open model families, which makes it suitable for mixed Chinese-English evaluation.

\textbf{Benchmark suite.} The baseline task suite includes MMLU for broad knowledge, GSM8K for mathematical reasoning, HumanEval or MBPP for code generation, C-Eval for Chinese evaluation, and one custom domain benchmark. The domain benchmark is intended to reflect the target application context of the paper and should be documented with data source, collection protocol, split statistics, and answer normalization rules. In the current implementation, the codebase supports both standardized harness-based evaluation for public benchmarks and JSONL-based local evaluation for the domain task.

\textbf{Decoding and measurement settings.} To ensure comparability, benchmark evaluation uses a unified decoding policy across models wherever possible. For efficiency measurement, each model is run on the same prompt set with fixed generation parameters. We record peak allocated and reserved GPU memory, per-prompt latency, and generated tokens per second. These measurements are taken after a short warm-up phase to reduce one-time initialization noise. Because real deployment decisions are sensitive to serving cost, these indicators are treated as first-class results rather than supplementary diagnostics.

\textbf{QLoRA setup.} The adaptation stage uses 4-bit quantization with NF4 and double quantization, together with LoRA adapters inserted into attention and feed-forward projection layers. The default recipe uses a fixed rank, LoRA scaling factor, dropout, batch size, gradient accumulation, warm-up ratio, maximum sequence length, and epoch count. These settings are held constant across adapted models unless a stability issue forces a documented change. The objective is not to tune each model exhaustively, but to compare how different model families respond to the same practical adaptation budget.

\textbf{Output artifacts.} For reproducibility, the implementation stores raw benchmark outputs, domain-evaluation generations, efficiency measurements, adapter checkpoints, and aggregated CSV summaries under a unified results directory. This design allows the same repository to support both experiment execution and paper writing: tables can be exported directly into the manuscript, while qualitative generations can be referenced during error analysis and discussion.

\input{tables/model_overview}
