Large language models (LLMs) have become a standard foundation for question answering, code generation, mathematical reasoning, and domain-specific assistant systems. However, the practical cost of deploying state-of-the-art models remains high. Many strong open models either require multiple high-memory GPUs or accept substantial latency penalties when served on commodity hardware. This creates a gap between benchmark-oriented model development and the deployment conditions actually available in most academic laboratories and applied engineering teams. In practice, a large share of model adoption still happens on a single workstation GPU, where memory, latency, and maintainability are binding constraints rather than secondary considerations.

This paper focuses on that deployment regime. Specifically, we study open LLMs up to 8B parameters under a fixed single-GPU resource budget represented by an NVIDIA RTX 3090 with 24GB of VRAM. The scope includes seven models from three widely used open families: Qwen3 models from 0.6B to 8B, Qwen2.5-7B-Instruct, DeepSeek-R1-Distill-Qwen-7B, and Gemma 3 4B. These models are representative for two reasons. First, they cover a practical scale range that can still be loaded and adapted on consumer hardware. Second, they reflect different design priorities, including lightweight dense instruction models and reasoning-oriented distilled variants.

The objective of this work is not to produce another static leaderboard. A pure ranking of benchmark scores provides limited value when the target deployment platform is fixed and resource-constrained. Instead, the central question is which model offers the best performance-efficiency tradeoff when memory headroom, inference throughput, and adaptation cost are jointly considered. This perspective is particularly important in Chinese academic and industrial contexts, where one often needs a model that can be evaluated locally, fine-tuned with moderate effort, and then integrated into a vertical application without access to large clusters.

To move beyond a score-only comparison, we organize the study as a closed-loop experimental pipeline. We first run unified baseline evaluations on general knowledge, mathematical reasoning, code generation, Chinese benchmarks, and a domain benchmark. We then measure deployment-oriented efficiency indicators, including peak VRAM, latency, and token throughput. Finally, we apply QLoRA~\cite{qlora} to selected models and re-evaluate them to determine whether low-cost adaptation can materially improve domain performance under the same hardware budget. This design makes the paper closer to a systems-and-application study than a benchmark note.

The main research questions are as follows:
\begin{enumerate}[leftmargin=1.5em]
  \item Which open models up to 8B parameters provide the best performance-efficiency tradeoff under a single 24GB GPU constraint?
  \item How much domain benefit can QLoRA provide without exceeding the memory budget of a single RTX 3090?
  \item Are there clear capability breakpoints across model scales for knowledge, reasoning, code, Chinese evaluation, and domain tasks?
  \item Do reasoning-oriented small models justify their additional inference cost in this deployment regime?
\end{enumerate}

The main contributions of this paper are summarized as follows.
\begin{enumerate}[leftmargin=1.5em]
  \item We present a reproducible single-GPU evaluation protocol for open LLMs up to 8B parameters, explicitly targeting a resource-constrained deployment scenario instead of an unconstrained benchmark scenario.
  \item We compare model utility along both task and systems dimensions, including general benchmark performance, Chinese capability, domain performance, peak memory usage, latency, and throughput.
  \item We implement a QLoRA-based adaptation pipeline and analyze whether domain-specific gains justify the additional training and serving cost under a 24GB VRAM budget.
  \item We provide model selection guidance for practitioners who need to choose between smaller instruct models and reasoning-oriented distilled models on commodity hardware.
\end{enumerate}

The rest of the paper is organized as follows. \Cref{sec:related_work} reviews prior research on open LLM evaluation, efficient adaptation, and resource-constrained deployment. \Cref{sec:methodology} describes the joint performance-efficiency analysis framework. \Cref{sec:experimental_setup} details the hardware, software, model pool, and benchmark suite. \Cref{sec:results} presents baseline, efficiency, and QLoRA results, followed by interpretation and limitations in \Cref{sec:discussion}. Finally, \Cref{sec:conclusion} concludes the paper.
