\label{sec:related_work}

Related work can be grouped into three closely connected directions: open LLM evaluation, parameter-efficient adaptation, and resource-constrained deployment.

\textbf{Open LLM evaluation.} Benchmark-oriented evaluation has become a standard way to compare open language models. Common benchmarks include MMLU for broad academic knowledge~\cite{mmlu}, GSM8K for grade-school mathematical reasoning~\cite{gsm8k}, HumanEval for code generation~\cite{humaneval}, and C-Eval for Chinese evaluation~\cite{ceval}. Open evaluation frameworks such as the Language Model Evaluation Harness~\cite{lm_eval} have improved reproducibility by standardizing prompts, decoding, and metrics across tasks. However, most public comparisons are still interpreted primarily as leaderboards. They typically emphasize final scores while leaving memory footprint, inference latency, and single-GPU deployment behavior either underreported or measured in inconsistent ways. This is a practical limitation because real model selection often depends on whether a model can be served and adapted inside a fixed hardware budget.

\textbf{Parameter-efficient adaptation.} Full-parameter fine-tuning is often infeasible for medium-sized language models on consumer GPUs. LoRA~\cite{lora} addresses this issue by injecting trainable low-rank matrices into the model while freezing the original weights. QLoRA~\cite{qlora} extends this idea by combining low-rank adaptation with 4-bit quantization, making it possible to fine-tune comparatively capable models within a much smaller memory footprint. The core attraction of QLoRA in our setting is not merely training efficiency, but the fact that it shifts domain adaptation from a cluster-scale problem to a workstation-scale problem. This makes it particularly relevant for scenarios where a small model must be quickly aligned to a specialized vertical domain.

\textbf{Resource-constrained deployment.} A growing body of work studies quantization, inference optimization, and efficient serving for LLMs. Much of this literature evaluates low-bit inference, KV-cache efficiency, or serving frameworks under throughput-oriented settings. These contributions are important, but they do not fully answer the model-selection question faced by many end users: given a single GPU and a modest domain adaptation budget, which model is most worthwhile to deploy? The answer depends on a multi-objective tradeoff among task quality, memory demand, latency, and fine-tuning benefit. Our work is positioned at this intersection. It combines benchmark evaluation and QLoRA adaptation under a fixed hardware budget so that the analysis remains directly relevant to real deployment decisions rather than abstract scaling trends alone.

Compared with prior work, the distinguishing feature of this study is the explicit coupling of three elements: a fixed single-GPU deployment regime, a mixed task suite that includes Chinese and domain-specific evaluation, and a closed-loop QLoRA adaptation analysis. This scope is deliberately narrower than open-ended leaderboard studies, but it is more informative for practical model selection under constrained resources.
