\label{sec:results}

\subsection{Result Availability}

The latest project plan is broader than the current result export. Therefore,
the tables below use two statuses: exported and placeholder. Exported rows are
read from existing CSV or JSON artifacts. Placeholder rows represent planned
experiments that should be filled before submission. This convention prevents
the paper from overstating incomplete evidence while still showing the full
experimental design.

\subsection{Public Benchmark Results}

\Cref{tab:public-results} summarizes the current int4 public benchmark rows
aligned with the ten-model plan. Qwen3-8B is currently the strongest exported
row, with 0.717 on MMLU, 0.782 on C-Eval, 0.659 on HumanEval, and a four-task
average of 0.539. Qwen3-4B obtains 0.668 on MMLU, 0.689 on C-Eval, 0.585 on
HumanEval, and a four-task average of 0.486. GSM8K is zero in the current
exports and should be rechecked with the final prompt and answer-extraction
policy before drawing conclusions about mathematical reasoning.

\input{tables/main_results}

The remaining public rows are placeholders:
\placeholder{run the ten-model int4 public benchmark sweep and regenerate
Table~\ref{tab:public-results}}.

\subsection{Railway-Domain Results}

\Cref{tab:domain-results} reports the exported int4 baseline rows for
Domain-QA and Domain-RegQA. On Domain-QA, Qwen3-8B reaches 0.317
character-level F1 and 0.158 token-level F1, while Qwen3-4B reaches 0.294
character-level F1 and 0.168 token-level F1. The length-ratio values show that
both models often produce answers longer than the reference, especially
Qwen3-4B on Domain-QA.

Domain-RegQA is substantially harder. Both exported baselines have zero exact
match and near-zero token-level F1. Qwen3-8B has a higher character-level F1
than Qwen3-4B (0.133 versus 0.077), but neither model provides reliable
evidence-grounded regulatory answers in the current baseline setting. This
supports the need for Domain-RegQA-specific or mixed-data QLoRA adaptation.

\input{tables/domain_results}

The missing domain rows are placeholders:
\placeholder{evaluate all ten models on Domain-QA and Domain-RegQA under the
same decoding and normalization settings}.

\subsection{Efficiency Results}

\Cref{tab:efficiency-results} reports the current int4 efficiency exports.
Qwen3-4B and Qwen3-8B have the lowest exported peak allocated memory among the
formal ten-model rows, at 2.55GB and 5.78GB respectively. Their throughput is
similar in the current int4 run, around 22 tokens/s. Qwen2.5-7B-Instruct and
DeepSeek-R1-Distill-Qwen-7B are faster in the exported int4 efficiency rows
(about 31 tokens/s), but their peak allocated memory is much higher at 13.64GB.

\input{tables/efficiency_results}

These measurements confirm that quantization must be evaluated on the actual
hardware and backend. A smaller memory footprint does not automatically imply
the best latency, and a fast 7B-class run may still leave less VRAM margin for
serving, batching, or adapters.

\subsection{QLoRA Training Results}

\Cref{tab:qlora-training-results} reports completed Adapter-A training
artifacts. Qwen2.5-7B-Instruct trains for three epochs in 17,987 seconds with
training loss 0.464 and evaluation loss 0.494. Qwen3-8B trains for three
epochs in 24,052 seconds with training loss 0.488 and evaluation loss 0.507.
Both runs fit the single RTX 3090 workflow and provide evidence that QLoRA is
operational for the selected model sizes.

\input{tables/qlora_training_results}

Adapter-B, Adapter-C, and Adapter-D remain planned:
\placeholder{train Domain-RegQA-only, mixed-data, and completion-only QLoRA
variants}.

\subsection{Adaptation Evaluation}

\Cref{tab:qlora-results} shows the current before/after comparison state. The
exported Qwen2.5-7B-Instruct Adapter-A row is evaluated on the full Domain-QA
test split. It reaches 0.163 character-level F1 and 0.420 reference
containment, while preserving public benchmark scores of 0.711 on MMLU and
0.785 on C-Eval. However, exact match remains zero and the output length ratio
is high in the raw export, indicating that the adapter needs stronger decoding
or loss-masking control before it can be treated as a domain solution.

\input{tables/qlora_results}

The final adaptation claim requires direct baseline-versus-adapter comparisons
for the same model, precision, prompt template, and decoding settings:
\placeholder{complete matched baseline, Adapter-A, Adapter-B, Adapter-C, and
Adapter-D evaluations}.

\subsection{Data-Composition Ablation Plan}

\Cref{tab:ablation-plan} preserves the planned ablation matrix. This table is
included now because it determines the structure of the final paper: the
central adaptation question is whether railway terminology data, regulatory
evidence data, mixed data, or completion-only loss masking produces the best
domain behavior without damaging public benchmark quality.

\input{tables/ablation_plan}
